### 2024-08-29 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.rmd
implemented code review suggested changes

```{r Hypothesis4ModelInitial, include = FALSE}
## Hypothesis 4 beta regression model
# running the model with none revised QMP ratio's
H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)

@@

```{r Hypothesis5ModelInitial, include = FALSE}
## Hypothesis 5 logistic regression model
H5_test_results <- apa_print(glm(hypothesis_support ~ QMP_ratio, data = data_h5, family = binomial))

@@

```{r Hypothesis6ModelInitial, include = FALSE}
## Hypothesis 6 beta regression model
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

@@

```{r H6ExploratoryAssociationsInitialTable, warning = FALSE}
# creating the dataframe for the table
H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
  Results_H6_between$op_def, Results_H6_between$op_op, Results_H6_between$op_sel, 
  Results_H6_between$op_quant, Results_H6_between$op_mod, Results_H6_between$sel_def, 
  Results_H6_between$sel_op, Results_H6_between$sel_sel, Results_H6_between$sel_quant, 
  Results_H6_between$sel_mod)

H6_table_dataframe_r <- rbind(Results_H6_between$quant_def, Results_H6_between$quant_op,
  Results_H6_between$quant_sel, Results_H6_between$quant_quant, Results_H6_between$quant_mod, 
  Results_H6_between$mod_def, Results_H6_between$mod_op, Results_H6_between$mod_sel, 
  Results_H6_between$mod_quant, Results_H6_between$mod_mod, Results_H6_between$tot_def, 
  Results_H6_between$tot_op, Results_H6_between$tot_sel, Results_H6_between$tot_quant, 
  Results_H6_between$tot_mod)

@@

# adding asterices for significance to the significant p in the dataframe
H6_table_dataframe[8,3] <- paste0(H6_table_dataframe[8,3], "$^*$")
H6_table_dataframe[11,3] <- paste0(H6_table_dataframe[11,3], "$^*$")
H6_table_dataframe[14,3] <- paste0(H6_table_dataframe[14,3], "$^*$")
H6_table_dataframe[8,6] <- paste0(H6_table_dataframe[8,6], "$^*$")
H6_table_dataframe[9,6] <- paste0(H6_table_dataframe[9,6], "$^*$")
H6_table_dataframe[11,6] <- paste0(H6_table_dataframe[11,6], "$^*$")
H6_table_dataframe[13,6] <- paste0(H6_table_dataframe[13,6], "$^*$")

# adding a column to help indicate the original QMP type
H6_table_dataframe_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe)

>>>>

```{r Hypothesis4ModelInitial, include = FALSE}
## Hypothesis 4 beta regression model
data_h4 <- rbind(data_h456_original, data_h456_replications)

# running the model with none revised QMP ratio's
H4_test_results <- betareg(QMP_ratio ~ rep_org, data = data_h4)

@@

```{r Hypothesis5ModelInitial, include = FALSE}
## Hypothesis 5 logistic regression model
# first removing any hypotheses from the data that were rated as being unclear
data_h5 <- data_h456_replications
data_h5 <- data_h5[data_h5$hypothesis_support != "Unclear",]
data_h5$hypothesis_support <- droplevels.factor(data_h5$hypothesis_support)

# running the model using the QMPs from the initial coding protocol
H5_test_results <- apa_print(glm(hypothesis_support ~ QMP_ratio, data = data_h5, family = binomial))

@@

```{r Hypothesis6ModelInitial, include = FALSE}
## Hypothesis 6 beta regression model
# first we combine the datasets of the original studies and the replications 
# together
# adding "Rep_" to separate replication from original columns in the combined dataset
data_h456_Rep <- data_h456_replications
colnames(data_h456_Rep) <- paste0("Rep_", colnames(data_h456_Rep))

# combine the dataset
data_h6 <- cbind(data_h456_original, data_h456_Rep)

# running the model using the QMPs from the initial coding protocol
H6_test_results <- betareg(Rep_QMP_ratio ~ QMP_ratio, data = data_h6)

@@

```{r Hypothesis6Associations, warning = FALSE}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (original QMP coding) MOVE THIS ANALYSIS TO INITIAL CODING APPENDIX
Results_H6_between <- Associations_H6(data_h456_replications[59:76], 
                                      data_h456_original[59:76])

# keep in mind mod_ratio (not Rep) is based on a very small sample size, less
# of a concern for the revised.
```

```{r H6ExploratoryAssociationsInitialTable, warning = FALSE}
# creating the dataframe for the table
H6_table_dataframe_l <- rbind(Results_H6_between$def_def, Results_H6_between$def_op,
  Results_H6_between$def_sel, Results_H6_between$def_quant, Results_H6_between$def_mod, 
  Results_H6_between$def_tot, Results_H6_between$op_def, Results_H6_between$op_op, 
  Results_H6_between$op_sel, Results_H6_between$op_quant, Results_H6_between$op_mod, 
  Results_H6_between$op_tot, Results_H6_between$sel_def, Results_H6_between$sel_op, 
  Results_H6_between$sel_sel, Results_H6_between$sel_quant, Results_H6_between$sel_mod, 
  Results_H6_between$sel_tot)

H6_table_dataframe_r <- rbind(Results_H6_between$quant_def, Results_H6_between$quant_op,
  Results_H6_between$quant_sel, Results_H6_between$quant_quant, Results_H6_between$quant_mod, 
  Results_H6_between$quant_tot, Results_H6_between$mod_def, Results_H6_between$mod_op, 
  Results_H6_between$mod_sel, Results_H6_between$mod_quant, Results_H6_between$mod_mod, 
  Results_H6_between$mod_tot, Results_H6_between$tot_def, Results_H6_between$tot_op, 
  Results_H6_between$tot_sel, Results_H6_between$tot_quant, Results_H6_between$tot_mod, 
  Results_H6_between$tot_tot)

@@

# adding asterices for significance to the significant p in the dataframe
H6_table_dataframe[9,3] <- paste0(H6_table_dataframe[9,3], "$^*$")
H6_table_dataframe[13,3] <- paste0(H6_table_dataframe[13,3], "$^*$")
H6_table_dataframe[16,3] <- paste0(H6_table_dataframe[16,3], "$^*$")
H6_table_dataframe[7,6] <- paste0(H6_table_dataframe[7,6], "$^*$")
H6_table_dataframe[9,6] <- paste0(H6_table_dataframe[9,6], "$^*$")
H6_table_dataframe[13,6] <- paste0(H6_table_dataframe[13,6], "$^*$")
H6_table_dataframe[15,6] <- paste0(H6_table_dataframe[15,6], "$^*$")

# adding a column to help indicate the original QMP type
H6_table_dataframe_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total"), H6_table_dataframe)

### 2024-08-29 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_item_reduced_measures_analyses.Rmd
implemented code review suggested changes

item_number_change_data <- coded_data_replications[!is.na(coded_data_replications$mod_5_REV) & coded_data_replications$mod_5_REV, c(1, 2, 3, 56)]

@@

```{r ReplicationSuccessDifferent}
# getting information on hypothesis support/replication success
hypothesis_support_index <- coded_data_replications$hypothesis_support

hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "Yes"

# coding Unclear into No instead of Yes didn't make a difference on the test.
# hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "No"

# chi-squared test of differences in hypothesis support/replication success 
# between measures for which items were decreased and for which it was not.
decreased_items_replicability_impact_test <- chisq.test(decreased_items_index, coded_data_replications$hypothesis_support)

@@

```{r H1Difference}
# H1
coded_data_original_shortened$reliability_type[decreased_items_index]
coded_data_replications$reliability_type[decreased_items_index]
```

@@

```{r H2H3Difference}
# H2 & H3
coded_data_original_shortened$reliability_coeff[decreased_items_index]
coded_data_replications$reliability_coeff[decreased_items_index]

# running the H3 model
data_h3_avg[data_h3_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]

@@

```{r OriginalQMPDIfference}
# comparing the mean and sd original QMP ratio 
print(c("mean decreased" = mean(data_h6$QMP_REV_ratio[decreased_items_index]),
      "sd decreased" = sd(data_h6$QMP_REV_ratio[decreased_items_index]),

@@

```{r H4Difference}
# running the h4 models
# only decreased item measures
betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4[c(decreased_items_index, decreased_items_index),]))

@@

```{r H5Difference}
# running the h5 models
apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5[decreased_items_index[c(53:55)],], family = binomial))$full_result$QMP_REV_ratio

>>>>

item_number_change_data <- data_h456_replications[!is.na(data_h456_replications$mod_5_REV) & data_h456_replications$mod_5_REV, c(1, 2, 3, 56)]

@@

```{r ReplicationSuccessDifferent}
# getting information on hypothesis support/replication success
hypothesis_support_index <- data_h456_replications$hypothesis_support

hypothesis_support_index[data_h456_replications$hypothesis_support == "Unclear"] <- "Yes"

# coding Unclear into No instead of Yes didn't make a difference on the test.
# hypothesis_support_index[data_h456_replications$hypothesis_support == "Unclear"] <- "No"

# chi-squared test of differences in hypothesis support/replication success 
# between measures for which items were decreased and for which it was not.
decreased_items_replicability_impact_test <- chisq.test(decreased_items_index, data_h456_replications$hypothesis_support)

@@

```{r H1Difference}
# H1
data_h456_original$reliability_type[decreased_items_index]
data_h456_replications$reliability_type[decreased_items_index]
```

@@

```{r H2H3Difference}
# H2 & H3
data_h456_original$reliability_coeff[decreased_items_index]
data_h456_replications$reliability_coeff[decreased_items_index]

# running the H3 model
data_h23_avg[data_h23_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]

@@

```{r OriginalQMPDIfference}
# first we combine the datasets of the original studies and the replications 
# together
# adding "Rep_" to separate replication from original columns in the combined dataset
data_h456_Rep <- data_h456_replications
colnames(data_h456_Rep) <- paste0("Rep_", colnames(data_h456_Rep))

# combine the dataset
data_h6 <- cbind(data_h456_original, data_h456_Rep)

# comparing the mean and sd original QMP ratio 
print(c("mean decreased" = mean(data_h6$QMP_REV_ratio[decreased_items_index]),
      "sd decreased" = sd(data_h6$QMP_REV_ratio[decreased_items_index]),

@@

```{r H4Difference}
# for H4 we have to combine the replication and original data together
data_h4 <- rbind(data_h456_original, data_h456_replications)

# running the h4 models
# only decreased item measures
betareg_output_to_apa_full(betareg(QMP_REV_ratio ~ rep_org, data = data_h4[c(decreased_items_index, decreased_items_index),]))

@@

```{r H5Difference}
## running the h5 models
# first removing any hypotheses from the data that were rated as being unclear
data_h5 <- data_h456_replications
data_h5 <- data_h5[data_h5$hypothesis_support != "Unclear",]
data_h5$hypothesis_support <- droplevels.factor(data_h5$hypothesis_support)

# running the model using the QMPs from the revised coding protocol
apa_print(glm(hypothesis_support ~ QMP_REV_ratio, data = data_h5[decreased_items_index[c(53:55)],], family = binomial))$full_result$QMP_REV_ratio

### 2024-08-29 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_multilevel_analyses.rmd
implemented code review suggested changes

This appendix contains the multilevel model versions of the models used to test Hypothesis 3, 5, & 6 in the main text (additional multilevel models can be found in [Supplementary Analyses C](Supplementary_omega_analyses.Rmd) and [Supplementary Analyses D](Supplementary_initial_QMP_analyses.Rmd)). These models were omitted from the main text because the sample sizes were not large enough to support multilevel modelling. Guidelines suggest to have at least within the range of 10 to 30 groups with 10 to 30 cases each for multilevel models, with more groups and cases each being necessary for more complex models, such as random-slope models (Kreft, 1996; Snijders and Bosker, 1993; Hox, 1998, 2010). For Hypothesis 3 we had `r nrow(table(data_h3_multiple$g))` groups with on average `r round(mean(table(data_h3_multiple$g)),3)` cases. For Hypothesis 5 and 6 we had `r nrow(table(coded_data_replications$many_labs_version))` groups with on average `r mean(table(coded_data_replications$many_labs_version))` cases. Therefore, while we have may have had a sufficient number of cases per group for simple models, we likely lacked a sufficient number of groups to estimate multilevel models, especially more complex models. In 4 (all random slope models) of the 12 multilevel models we ran we encountered convergence issues, further illustrating that our sample size was likely inadequate for these models.

@@

```{r Hypothesis3MultilevelModelSensitivityAnalyses, warning = FALSE}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h3_multiple))

@@

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

@@

```{r Hypotheses5And6SensitivityAnalyses, warning = FALSE}
## Hypothesis 5 sensitivity test using a random intercept and random slope Gaussian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h5

>>>>

This appendix contains the multilevel model versions of the models used to test Hypothesis 3, 5, & 6 in the main text (additional multilevel models can be found in [Supplementary Analyses C](Supplementary_omega_analyses.Rmd) and [Supplementary Analyses D](Supplementary_initial_QMP_analyses.Rmd)). These models were omitted from the main text because the sample sizes were not large enough to support multilevel modelling. Guidelines suggest to have at least within the range of 10 to 30 groups with 10 to 30 cases each for multilevel models, with more groups and cases each being necessary for more complex models, such as random-slope models (Kreft, 1996; Snijders and Bosker, 1993; Hox, 1998, 2010). For Hypothesis 3 we had `r nrow(table(data_h23$g))` groups with on average `r round(mean(table(data_h23$g)),3)` cases. For Hypothesis 5 and 6 we had `r nrow(table(data_h456_replications$many_labs_version))` groups with on average `r mean(table(data_h456_replications$many_labs_version))` cases. Therefore, while we have may have had a sufficient number of cases per group for simple models, we likely lacked a sufficient number of groups to estimate multilevel models, especially more complex models. In 4 (all random slope models) of the 12 multilevel models we ran we encountered convergence issues, further illustrating that our sample size was likely inadequate for these models.

@@

```{r Hypothesis3MultilevelModelSensitivityAnalyses, warning = FALSE}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- apa_print(glmer(formula = replication_success ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_h23))

@@

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_alpha <- apa_print(glmer(formula = replication_success ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                data_h23))

@@

```{r Hypotheses5And6SensitivityAnalyses, warning = FALSE}
## Hypothesis 5 sensitivity test using a random intercept and random slope Gaussian model.
# create dummy H5 dataframe for use in sensitivity test
data_h5_sens <- data_h456_replications
data_h5_sens <- data_h5_sens[data_h5_sens$hypothesis_support != "Unclear",]
data_h5_sens$hypothesis_support <- droplevels.factor(data_h5_sens$hypothesis_support)

### 2024-08-29 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_omega_analyses.rmd
implemented code review suggested changes

```{r Hypothesis2ModelOmega, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_omega <- lmer(formula = omega ~ 1 + (1|g), data = data_h2[complete.cases(data_h2),])

@@

```{r Hypothesis3MainTestOmega, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_omega <- apa_print(glm(formula = replication ~ 1 + 
                                     omega, family = binomial(), 
                                     data = data_h3_avg))

@@

```{r Hypothesis3MultilevelModelSensitivityAnalysesOmega}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
                                                + omega + (1|g), family = 
                                                  binomial(), data = 
                                                  data_h3_multiple))

@@

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_omega <- apa_print(glmer(formula = replication ~ 1 
                                                + omega + (1 + omega|g), 
                                                family = binomial(), data =
                                                data_h3_multiple))

@@

### Results & Comparison Interpretation
For omega the mean (values calculated in the population across replication sets) was `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.

@@

Thus, no evidence in favor of Hypothesis 3 was found. However, caution in interpreting the test results is needed. The number of measures for which the omega coefficient could be and was calculated was quite low (`r apa_num(sum(!is.na(data_h3_avg$omega)), numerals = FALSE)`).

>>>>

```{r Hypothesis2ModelOmega, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_omega <- lmer(formula = omega ~ 1 + (1|g), data = data_h23[complete.cases(data_h23),])

@@

```{r Hypothesis3MainTestOmega, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_omega <- apa_print(glm(formula = replication_success ~ 1 + 
                                     omega, family = binomial(), 
                                     data = data_h23_avg))

@@

```{r Hypothesis3MultilevelModelSensitivityAnalysesOmega}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_omega <- apa_print(glmer(formula = replication_success ~ 1 
                                                + omega + (1|g), family = 
                                                  binomial(), data = 
                                                  data_h23))

@@

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_omega <- apa_print(glmer(formula = replication_success ~ 1 
                                                + omega + (1 + omega|g), 
                                                family = binomial(), data =
                                                data_h23))

@@

### Results & Comparison Interpretation
For omega the mean (values calculated in the population across replication sets) was `r apa_num(mean(data_h23$omega, na.rm = TRUE), digits = 3)` with a standard deviation of `r apa_num(sd(data_h23$omega, na.rm = TRUE), digits = 3)`.

@@

Thus, no evidence in favor of Hypothesis 3 was found. However, caution in interpreting the test results is needed. The number of measures for which the omega coefficient could be and was calculated was quite low (`r apa_num(sum(!is.na(data_h23$omega)), numerals = FALSE)`).

### 2024-08-29 SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd
implemented code review suggested changes

```{r Hypothesis2Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h2)

@@

```{r Hypothesis6Associations, warning = FALSE}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (original QMP coding) MOVE THIS ANALYSIS TO INITIAL CODING APPENDIX
Results_H6_between <- Associations_H6(data_h6)

# keep in mind mod_ratio (not Rep) is based on a very small sample size, less
# of a concern for the revised.

# Associations between the QMP categories (revised QMP coding)
Results_H6_between_REV <- Associations_H6_REV(data_h6)

@@

```{r H6ExploratoryAssociationsRevisedTable, warning = FALSE}
# creating the dataframe for the table
H6_table_dataframe_l_REV <- rbind(Results_H6_between_REV$def_def, Results_H6_between_REV$def_op,
  Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
  Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, Results_H6_between_REV$op_sel, 
  Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, Results_H6_between_REV$sel_def, 
  Results_H6_between_REV$sel_op, Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, 
  Results_H6_between_REV$sel_mod)

H6_table_dataframe_r_REV <- rbind(Results_H6_between_REV$quant_def, Results_H6_between_REV$quant_op,
  Results_H6_between_REV$quant_sel, Results_H6_between_REV$quant_quant, Results_H6_between_REV$quant_mod, 
  Results_H6_between_REV$mod_def, Results_H6_between_REV$mod_op, Results_H6_between_REV$mod_sel, 
  Results_H6_between_REV$mod_quant, Results_H6_between_REV$mod_mod, Results_H6_between_REV$tot_def, 
  Results_H6_between_REV$tot_op, Results_H6_between_REV$tot_sel, Results_H6_between_REV$tot_quant, 
  Results_H6_between_REV$tot_mod)

@@

# adding asterices for significance to the significant p in the dataframe
H6_table_dataframe_REV[11,3] <- paste0(H6_table_dataframe_REV[11,3], "$^*$")
H6_table_dataframe_REV[13,3] <- paste0(H6_table_dataframe_REV[13,3], "$^*$")
H6_table_dataframe_REV[14,3] <- paste0(H6_table_dataframe_REV[14,3], "$^*$")
H6_table_dataframe_REV[4,6] <- paste0(H6_table_dataframe_REV[4,6], "$^*$")
H6_table_dataframe_REV[11,6] <- paste0(H6_table_dataframe_REV[11,6], "$^*$")
H6_table_dataframe_REV[13,6] <- paste0(H6_table_dataframe_REV[13,6], "$^*$")
H6_table_dataframe_REV[14,6] <- paste0(H6_table_dataframe_REV[14,6], "$^*$")

# adding a column to help indicate the original QMP type
H6_table_dataframe_REV_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Definition", "Operationalisation", "Selection", "Quantification", "Modification"), H6_table_dataframe_REV)

>>>>

```{r Hypothesis2Model, include = FALSE}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- lmer(formula = alpha ~ 1 + (1|g), data = data_h23)

@@

```{r Hypothesis6Associations, warning = FALSE}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (revised QMP coding)
Results_H6_between_REV <- Associations_H6(data_h456_replications[c(59:61, 77:91)], 
                                      data_h456_original[c(59:61, 77:91)])

# keep in mind mod_ratio (not Rep) is based on a somewhat small sample size
```

@@

```{r H6ExploratoryAssociationsRevisedTable, warning = FALSE}
# creating the dataframe for the table
H6_table_dataframe_l_REV <- rbind(Results_H6_between_REV$def_def, Results_H6_between_REV$def_op,
  Results_H6_between_REV$def_sel, Results_H6_between_REV$def_quant, Results_H6_between_REV$def_mod, 
  Results_H6_between_REV$def_tot, Results_H6_between_REV$op_def, Results_H6_between_REV$op_op, 
  Results_H6_between_REV$op_sel, Results_H6_between_REV$op_quant, Results_H6_between_REV$op_mod, 
  Results_H6_between_REV$op_tot, Results_H6_between_REV$sel_def, Results_H6_between_REV$sel_op, 
  Results_H6_between_REV$sel_sel, Results_H6_between_REV$sel_quant, Results_H6_between_REV$sel_mod, 
  Results_H6_between_REV$sel_tot)

H6_table_dataframe_r_REV <- rbind(Results_H6_between_REV$quant_def, Results_H6_between_REV$quant_op,
  Results_H6_between_REV$quant_sel, Results_H6_between_REV$quant_quant, Results_H6_between_REV$quant_mod, 
  Results_H6_between_REV$quant_tot, Results_H6_between_REV$mod_def, Results_H6_between_REV$mod_op, 
  Results_H6_between_REV$mod_sel, Results_H6_between_REV$mod_quant, Results_H6_between_REV$mod_mod, 
  Results_H6_between_REV$mod_tot, Results_H6_between_REV$tot_def, Results_H6_between_REV$tot_op, 
  Results_H6_between_REV$tot_sel, Results_H6_between_REV$tot_quant, Results_H6_between_REV$tot_mod, 
  Results_H6_between_REV$tot_tot)

@@

# adding asterices for significance to the significant p in the dataframe
H6_table_dataframe_REV[13,3] <- paste0(H6_table_dataframe_REV[13,3], "$^*$")
H6_table_dataframe_REV[15,3] <- paste0(H6_table_dataframe_REV[15,3], "$^*$")
H6_table_dataframe_REV[16,3] <- paste0(H6_table_dataframe_REV[16,3], "$^*$")
H6_table_dataframe_REV[18,3] <- paste0(H6_table_dataframe_REV[18,3], "$^*$")
H6_table_dataframe_REV[4,6] <- paste0(H6_table_dataframe_REV[4,6], "$^*$")
H6_table_dataframe_REV[13,6] <- paste0(H6_table_dataframe_REV[13,6], "$^*$")
H6_table_dataframe_REV[15,6] <- paste0(H6_table_dataframe_REV[15,6], "$^*$")
H6_table_dataframe_REV[16,6] <- paste0(H6_table_dataframe_REV[16,6], "$^*$")

# adding a column to help indicate the original QMP type
H6_table_dataframe_REV_expanded <- cbind(c("Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total", "Definition", "Operationalisation", "Selection", "Quantification", "Modification", "Total"), H6_table_dataframe_REV)
